Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
update authors and affil; start with ngc 2419 intro

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{
Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

@@

\section{Introduction}
The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation. Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the underestimation of K abundance predicted by models \citep{kobayashi2011}. Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.

NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gy \citep{forbesandbridges2010}. It resides in the outer halo 87.5 kpc (original source unknown) from the galactic centre, and its chemical make-up makes it one of the most unusual clusters in the galaxy.

>>>>

\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{#1}}

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{
Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
Andrew R. Casey,$^{1,2}$
%Matthew Miles? (Monash)
%Brodie Norfolk? (Monash)
%Amanda Karakas? (Monash)
%John Lattanzio? (Monash)
%Kevin Schlaufman? (JHU)
%Anna Ho? (Caltech)
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
}

% These dates will be filled out by the publisher
\date{Accepted 2018 XX XX. Received 2018 YY YY; in original form 2018 ZZ ZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

@@

\section{Introduction}

NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gyr \citep{forbesandbridges2010}. It resides in the outer halo 87.5 kpc \todo{[citation needed]} from the galactic centre, and its chemical make-up makes it one of the most unusual clusters in the galaxy.

The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation. Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the underestimation of K abundance predicted by models \citep{kobayashi2011}. Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
